---
title: "Diamond sizes"
date: 2016-08-25
output: html_document
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)

knitr::opts_chunk$set(echo = FALSE)

comma <- function(x) format(x, digits = 2, big.mark = ",")

smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

We have data about `r comma(nrow(diamonds))` diamonds. Only 
`r (n_larger <- nrow(diamonds) - nrow(smaller))` 
(`r scales::percent(n_larger/nrow(diamonds), accuracy = 0.01)`) 
are larger than 2.5 carats. The distribution of the remainder 
is shown below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

## Size by cut, colour and clarity

There is no strong correlation between size and cut.

```{r}
ggplot(diamonds) +
  geom_boxplot(aes(cut, carat))
```

Heavier diamonds tend to have a bad color and clarity.

```{r}
ggplot(diamonds) +
  geom_boxplot(aes(color, carat))

ggplot(diamonds) +
  geom_boxplot(aes(clarity, carat))
```

## Largest 20 diamonds

```{r}
diamonds %>% 
  arrange(desc(carat)) %>% 
  slice(1:20) %>% 
  group_by(cut) %>% 
  summarise_if(is.numeric, median) %>% 
  knitr::kable(
    caption = "Median values, by cut."
    )
```

## Network of chunks

```{r a, cache=TRUE}
lubridate::now()
```

```{r b, cache=TRUE, dependson="a"}
lubridate::now()
```

```{r c, cache=TRUE, dependson="a"}
lubridate::now()
```

```{r d, cache=TRUE, dependson=c("b", "c")}
lubridate::now()
```

```{r}
lubridate::now()
```
